What We Eval in the Shadows

### 2021-04-16 paper/main.tex
Grammarly's proofreading of Section V.3 (origins)

Where does the expression passed to \eval come from? There are various means of
creating that expression, these are associated with particular use cases, we
classify them in three categories:

\begin{compactitem}[---]
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote}, \c{expression}. Function arguments are passed as
  promises and \c{substitute} is used to retrieve the source expression
  associated with the promise.
  \item {\it Reflection:} This group corresponds to uses of the \c{match.call}
  function to reflectively capture the expression that invoked the current
  function.
\item {\it String:} Finally, expressions can be created from strings by invoking
   \c{parse}, \c{str2expression} or \c{str2lang}.
\end{compactitem}

\noindent
Table~\ref{tab:provenance} summarizes the expression provenance in our corpus.
This data is obtained by dynamically tainting values as they are produced by the
various sources, due to technical reasons, there is some imprecision in the
results. In particular, we are not able to classify all sites. Manual inspection
of numerous examples suggest that the classified results are accurate.

@@

Strings could correlate with dynamic code loading. This is what the base
functions \c{source} and \c{sys.source} do. We observed few calls
(\packageNbParseFromFileSites in total) that consume the result of calling
\c{parse} on a file. Most of the calls build strings programmatically. We also
identified one function \c{invokeRestartInteractively} that prompts the user for
input, parses it, and passes it to \eval. The use of strings seems to correlate
with less sophisticated programmers; in our Kaggle corpus
\kaggleParseExprsSitePercent of site use strings.

\paragraph{Discussion}
The origin data suggests that constructing expressions from strings is a
minority of the use cases, instead the constructed category shows that the
majority of \evals comes from code that was processed by the compiler, and may be
slightly modified by the programmer before invoking \eval. Both constructed and
reflection categories roughly correspond to meta-programming. Some of these use
cases could likely be replaced by macros if the R designers could be convinced
to overcome their distaste for those.

>>>>

Where does the expression passed to \eval come from? There are various means of
creating that expression, which are associated with particular use cases. We
classify them into three categories:

\begin{compactitem}[---]
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote}, \c{expression}. Function arguments are passed as
  promises, and \c{substitute} is used to retrieve the source expression
  associated with the promise.
  \item {\it Reflection:} This group corresponds to uses of the \c{match.call}
  function to reflectively capture the expression that invoked the current
  function.
\item {\it String:} Finally, expressions can be created from strings by invoking
   \c{parse}, \c{str2expression}, or \c{str2lang}.
\end{compactitem}

\noindent
Table~\ref{tab:provenance} summarizes the expression provenance in our corpus.
This data is obtained by dynamically tainting values as they are produced by the
various sources. Due to technical reasons, there is some imprecision in the
results. In particular, we are not able to classify all sites. Manual inspection
of numerous examples suggests that the classified results are accurate.

@@

Strings could correlate with dynamic code loading. This is what the base
functions \c{source} and \c{sys.source} do. We observed few calls
(\packageNbParseFromFileSites in total) that consume the result of calling
\c{parse} on a file. Most of the calls build strings programmatically. We also
identified one function \c{invokeRestartInteractively} that prompts the user for
input, parses it, and passes it to \eval. The use of strings seems to correlate
with less sophisticated programmers; in our Kaggle corpus,
\kaggleParseExprsSitePercent of sites use strings.

\paragraph{Discussion}
The origin data suggests that constructing expressions from strings is a
minority of the use cases. Instead, the constructed category shows that most \evals comes from code that was processed by the compiler, and may be
slightly modified by the programmer before invoking \eval. Both constructed and
reflection categories roughly correspond to meta-programming. Some of these use
cases could likely be replaced by macros if the R designers could be convinced
to overcome their distaste for those.
